What is disputed on the web?

### 2010-02-09 papers/wicow_claimfinder/claimfinder.tex

\begin{figure}[tbh]
 \begin{center}
  \begin{tabular}{|lll|}
    \hline
    {\bf Noun} & {\bf Word Cluster} & {\bf Freq} \\
    \hline
   {\bf children} & tiger woods abused & 218\\
                  & instead encourage daily & 178\\
    \hline
   {\bf god} & daily encourage parents & 150 \\
   \hline
   {\bf government} & health care & 1267 \\
                    & united states & 427 \\
		    & relation environmental matters & 155 \\
   \hline
   {\bf iraq} & weapons mass destruction & 373 \\
              & united states & 247 \\
	      & saddam hussein & 192 \\
	      & al qaeda & 149 \\
   \hline
   {\bf israel} & middle east & 251 \\
		& allowed upon population & 128 \\
                & united states & 107 \\
		& off map & 106 \\
   \hline
   {\bf law}    & lawbreaker rather broken & 133 \\
		& united states &\\
   \hline
    {\bf obama} & working best interests & 568\\
                & health care & 481\\
	        & united states & 327 \\
		& nobel prize & 270 \\
		& legitimately president & 207 \\
		& ford hood shooter hasan nidal advised & 190 \\
		& birth certificate & 180\\
   \hline
   {\bf president} & united states & 439 \\
                   & health care & 203 \\
		   & george w & 164 \\
		   & aircraft system jolting bombing & 159 \\
		   & peace prize & 125 \\
		   & white house & 125 \\
   \hline
      {\bf war} & united states & 340 \\
   \hline

>>>>

\begin{figure}[tbh]
 \begin{center}
  \begin{tabular}{|lll|}
    \hline
    {\bf Noun} & {\bf Word Cluster} & {\bf Freq} \\
    \hline
   {\bf children} & tiger woods abused & 218\\
                  & instead encourage daily & 178\\
    \hline
   {\bf god} & daily encourage parents & 150 \\
   \hline
   {\bf government} & health care & 1267 \\
                    & united states & 427 \\
		    & relation environmental matters & 155 \\
   \hline
   {\bf iraq} & weapons mass destruction & 373 \\
              & united states & 247 \\
	      & saddam hussein & 192 \\
	      & al qaeda & 149 \\
   \hline
   {\bf israel} & middle east & 251 \\
		& allowed upon population & 128 \\
                & united states & 107 \\
		& off map & 106 \\
   \hline
   {\bf law}    & lawbreaker rather broken & 133 \\
		& united states & 116\\
   \hline
    {\bf obama} & working best interests & 568\\
                & health care & 481\\
	        & united states & 327 \\
		& nobel prize & 270 \\
		& legitimately president & 207 \\
		& fort hood shooter hasan nidal advised & 190 \\
		& birth certificate & 180\\
   \hline
   {\bf president} & united states & 439 \\
                   & health care & 203 \\
		   & george w & 164 \\
		   & aircraft system jolting bombing & 159 \\
		   & peace prize & 125 \\
		   & white house & 125 \\
   \hline
      {\bf war} & united states & 340 \\
   \hline
